```{r}
# Import libraries
library(tm)
library(stringr)
library(wordcloud)
library(slam)
library(quanteda)
library(SnowballC)
library(arules)
library(proxy)
library(cluster)
library(stringi)
library(proxy)
library(Matrix)
library(tidytext) 
library(plyr) 
library(ggplot2)
library(factoextra) 
library(mclust)
library(textstem)
library(amap)
library(networkD3)
library(dplyr)
library(tcltk)
library(arulesViz)
```

# Song titles

## Hierarchical clustering

```{r}
# Read in data
# setwd("C:/Users/maede/Downloads/R/INFO5653/Project/Project/INFO5653_Project")

song_titles <- read.csv("lennon_mccartney_clean.csv")
#clean_song_titles <- song_titles[rowSums(song_titles[, -1]) != 0, ]

# Filter by label
lennon <- song_titles %>% filter(LABEL == 'john')
mccartney <- song_titles %>% filter(LABEL == 'paul')

# Sample for dendrograms
sample_lennon <- sample_n(lennon, 20)
sample_mccartney <- sample_n(mccartney, 20)

# Bind together
sample_song_titles <- rbind(sample_lennon, sample_mccartney)

# Save unlabeled data
song_titles_unlabeled <- sample_song_titles %>% select(-LABEL)

# Find distances
dist_matrix_E <- dist(song_titles_unlabeled, method="euclidean")

dist_matrix_C <- dist(song_titles_unlabeled, method="cosine")

dist_matrix_Min_1 <- dist(song_titles_unlabeled, method="manhattan", p=1)

# Hierarchical Clustering, Dendrogram

## Euclidean
groups_E <- hclust(dist_matrix_E,method="ward.D")
plot(groups_E, cex=0.9, hang=-1, main = "Euclidean", xlim = c(0, 10))
rect.hclust(groups_E, k=2)

## Cosine
groups_C <- hclust(dist_matrix_C,method="ward.D")
plot(groups_C, cex=0.9, hang=-1, main = "Cosine", xlim = c(0, 10))
rect.hclust(groups_C, k=2)

## Minkowski
groups_Min_1 <- hclust(dist_matrix_Min_1,method="ward.D")
plot(groups_Min_1, cex=0.9, hang=-1, main = "Manhattan", xlim = c(0, 10))
rect.hclust(groups_Min_1, k=2)
```

## K-means clustering

```{r}
song_titles <- read.csv("lennon_mccartney_clean.csv")
song_titles_unlabeled <- song_titles %>% select(-LABEL)

# K-means clustering
song_titles_matrix <- data.matrix(song_titles_unlabeled)

## Silhouette........................
fviz_nbclust(song_titles_matrix, method = "silhouette", 
             FUN = hcut, k.max = 9)

# for k = 2
## Run Kmeans...
My_Kmeans1 <- Kmeans(song_titles_matrix, centers = 2, iter.max = 1000, nstart = 4, method = "euclidean")
#, iter.max = 10, nstart = 1)
fviz_cluster(My_Kmeans1, song_titles_matrix, main="Euclidean")

My_Kmeans2 <- Kmeans(song_titles_matrix, centers = 2, iter.max = 1000, nstart = 4, method = "spearman")
fviz_cluster(My_Kmeans2, song_titles_matrix, main = "Spearman")

My_Kmeans3 <- Kmeans(song_titles_matrix, centers = 2, iter.max = 1000, method = "manhattan")
fviz_cluster(My_Kmeans3, song_titles_matrix, main ="Manhattan")

# for k = 2
## Run Kmeans...
My_Kmeans1 <- Kmeans(song_titles_matrix, centers = 4, iter.max = 1000, method = "euclidean")
#, iter.max = 10, nstart = 1)
fviz_cluster(My_Kmeans1, song_titles_matrix, main="Euclidean")

My_Kmeans2 <- Kmeans(song_titles_matrix, centers = 4, iter.max = 1000,method = "spearman")
fviz_cluster(My_Kmeans2, song_titles_matrix, main = "Spearman")

My_Kmeans3 <- Kmeans(song_titles_matrix, centers = 4, iter.max = 1000, method = "manhattan")
fviz_cluster(My_Kmeans3, song_titles_matrix, main ="Manhattan")
```

# Lyrics

## Hierarchical clustering

```{r}
# Read in data

# setwd("C:/Users/maede/Downloads/R/INFO5653/Project/Project/INFO5653_Project")
lyrics <- read.csv("paul_john_lyrics_corpus_count100.csv")

# Filter by label
lennon <- lyrics %>% filter(LABEL == 'Lennon')
mccartney <- lyrics %>% filter(LABEL == 'McCartney')

# Sample for dendrograms
sample_lennon <- sample_n(lennon, 20)
sample_mccartney <- sample_n(mccartney, 20)

# Bind together
sample_lyrics <- rbind(sample_lennon, sample_mccartney)

# Save unlabeled data
lyrics_unlabeled <- sample_lyrics %>% select(-LABEL)

# Find distances
dist_matrix_E <- dist(lyrics_unlabeled, method="euclidean")

dist_matrix_C <- dist(lyrics_unlabeled, method="cosine")

dist_matrix_Min_1 <- dist(lyrics_unlabeled, method="manhattan", p=1)

# Hierarchical Clustering, Dendrogram

## Euclidean
groups_E <- hclust(dist_matrix_E,method="ward.D")
plot(groups_E, cex=0.9, hang=-1, main = "Euclidean", xlim = c(0, 10))
rect.hclust(groups_E, k=2)

## Cosine
groups_C <- hclust(dist_matrix_C,method="ward.D")
plot(groups_C, cex=0.9, hang=-1, main = "Cosine", xlim = c(0, 10))
rect.hclust(groups_C, k=2)

## Minkowski
groups_Min_1 <- hclust(dist_matrix_Min_1,method="ward.D")
plot(groups_Min_1, cex=0.9, hang=-1, main = "Manhattan", xlim = c(0, 10))
rect.hclust(groups_Min_1, k=2)
```

## K-means clustering

```{r}
lyrics <- read.csv("paul_john_lyrics_corpus_count100.csv")
lyrics_unlabeled <- lyrics %>% select(-LABEL)

# K-means clustering
lyrics_matrix <- data.matrix(lyrics_unlabeled)

## Silhouette........................
fviz_nbclust(lyrics_matrix, method = "silhouette", 
             FUN = hcut, k.max = 9)


## Run Kmeans...
My_Kmeans1 <- Kmeans(lyrics_matrix, centers = 2, iter.max = 1000, method = "euclidean")
#, iter.max = 10, nstart = 1)
fviz_cluster(My_Kmeans1, lyrics_matrix, main="Euclidean")

My_Kmeans2 <- Kmeans(lyrics_matrix, centers = 2, iter.max = 1000, method = "spearman")
fviz_cluster(My_Kmeans2, lyrics_matrix, main = "Spearman")

My_Kmeans3 <- Kmeans(lyrics_matrix, centers = 2, iter.max = 1000, method = "manhattan")
fviz_cluster(My_Kmeans3, lyrics_matrix, main ="Manhattan")

```

# Lyrics lem

## Hierarchical clustering

```{r}
# Read in data

# setwd("C:/Users/maede/Downloads/R/INFO5653/Project/Project/INFO5653_Project")
lyrics <- read.csv("paul_john_lyrics_corpus_lem_count100.csv")

# Filter by label
lennon <- lyrics %>% filter(Label == 'Lennon')
mccartney <- lyrics %>% filter(Label == 'McCartney')

# Sample for dendrograms
sample_lennon <- sample_n(lennon, 20)
sample_mccartney <- sample_n(mccartney, 20)

# Bind together
sample_lyrics <- rbind(sample_lennon, sample_mccartney)

# Save unlabeled data
lyrics_unlabeled <- sample_lyrics %>% select(-Label)

# Find distances
dist_matrix_E <- dist(lyrics_unlabeled, method="euclidean")

dist_matrix_C <- dist(lyrics_unlabeled, method="cosine")

dist_matrix_Min_1 <- dist(lyrics_unlabeled, method="manhattan", p=1)

# Hierarchical Clustering, Dendrogram

## Euclidean
groups_E <- hclust(dist_matrix_E,method="ward.D")
plot(groups_E, cex=0.9, hang=-1, main = "Euclidean", xlim = c(0, 10))
rect.hclust(groups_E, k=2)

## Cosine
groups_C <- hclust(dist_matrix_C,method="ward.D")
plot(groups_C, cex=0.9, hang=-1, main = "Cosine", xlim = c(0, 10))
rect.hclust(groups_C, k=2)

## Minkowski
groups_Min_1 <- hclust(dist_matrix_Min_1,method="ward.D")
plot(groups_Min_1, cex=0.9, hang=-1, main = "Manhattan", xlim = c(0, 10))
rect.hclust(groups_Min_1, k=2)
```

## K-means clustering

```{r}
lyrics <- read.csv("paul_john_lyrics_corpus_lem_count100.csv")
lyrics_unlabeled <- lyrics %>% select(-Label)

# K-means clustering
lyrics_matrix <- data.matrix(lyrics_unlabeled)

## Silhouette........................
fviz_nbclust(lyrics_matrix, method = "silhouette", 
             FUN = hcut, k.max = 9)


## Run Kmeans...
My_Kmeans1 <- Kmeans(lyrics_matrix, centers = 2, iter.max = 1000, method = "euclidean")
#, iter.max = 10, nstart = 1)
fviz_cluster(My_Kmeans1, lyrics_matrix, main="Euclidean")

My_Kmeans2 <- Kmeans(lyrics_matrix, centers = 2, iter.max = 1000, method = "spearman")
fviz_cluster(My_Kmeans2, lyrics_matrix, main = "Spearman")

My_Kmeans3 <- Kmeans(lyrics_matrix, centers = 2, iter.max = 1000, method = "manhattan")
fviz_cluster(My_Kmeans3, lyrics_matrix, main ="Manhattan")

```

# Lyrics stem

## Hierarchical clustering

```{r}
# Read in data

# setwd("C:/Users/maede/Downloads/R/INFO5653/Project/Project/INFO5653_Project")
lyrics <- read.csv("paul_john_lyrics_corpus_stem_count100.csv")

# Filter by label
lennon <- lyrics %>% filter(Label == 'Lennon')
mccartney <- lyrics %>% filter(Label == 'McCartney')

# Sample for dendrograms
sample_lennon <- sample_n(lennon, 20)
sample_mccartney <- sample_n(mccartney, 20)

# Bind together
sample_lyrics <- rbind(sample_lennon, sample_mccartney)

# Save unlabeled data
lyrics_unlabeled <- sample_lyrics %>% select(-Label)

# Find distances
dist_matrix_E <- dist(lyrics_unlabeled, method="euclidean")

dist_matrix_C <- dist(lyrics_unlabeled, method="cosine")

dist_matrix_Min_1 <- dist(lyrics_unlabeled, method="manhattan", p=1)

# Hierarchical Clustering, Dendrogram

## Euclidean
groups_E <- hclust(dist_matrix_E,method="ward.D")
plot(groups_E, cex=0.9, hang=-1, main = "Euclidean", xlim = c(0, 10))
rect.hclust(groups_E, k=2)

## Cosine
groups_C <- hclust(dist_matrix_C,method="ward.D")
plot(groups_C, cex=0.9, hang=-1, main = "Cosine", xlim = c(0, 10))
rect.hclust(groups_C, k=2)

## Minkowski
groups_Min_1 <- hclust(dist_matrix_Min_1,method="ward.D")
plot(groups_Min_1, cex=0.9, hang=-1, main = "Manhattan", xlim = c(0, 10))
rect.hclust(groups_Min_1, k=2)
```

## K-means clustering

```{r}
lyrics <- read.csv("paul_john_lyrics_corpus_stem_count100.csv")
lyrics_unlabeled <- lyrics %>% select(-Label)

# K-means clustering
lyrics_matrix <- data.matrix(lyrics_unlabeled)

## Silhouette........................
fviz_nbclust(lyrics_matrix, method = "silhouette", 
             FUN = hcut, k.max = 9)


## Run Kmeans...
My_Kmeans1 <- Kmeans(lyrics_matrix, centers = 2, iter.max = 1000, method = "euclidean")
#, iter.max = 10, nstart = 1)
fviz_cluster(My_Kmeans1, lyrics_matrix, main="Euclidean")

My_Kmeans2 <- Kmeans(lyrics_matrix, centers = 2, iter.max = 1000, method = "spearman")
fviz_cluster(My_Kmeans2, lyrics_matrix, main = "Spearman")

My_Kmeans3 <- Kmeans(lyrics_matrix, centers = 2, iter.max = 1000, method = "manhattan")
fviz_cluster(My_Kmeans3, lyrics_matrix, main ="Manhattan")

```

# News articles descriptions

## Hierarchical clustering

```{r}
# Read in data

# setwd("C:/Users/maede/Downloads/R/INFO5653/Project/Project/INFO5653_Project")
description <- read.csv("paul_john_description_clean.csv")


# Save unlabeled data
description_unlabeled <- description %>% select(-Label)


# Find distances
dist_matrix_E <- dist(description_unlabeled, method="euclidean")

dist_matrix_C <- dist(description_unlabeled, method="cosine")

dist_matrix_Min_1 <- dist(description_unlabeled, method="manhattan", p=1)

# Hierarchical Clustering, Dendrogram

## Euclidean
groups_E <- hclust(dist_matrix_E,method="ward.D")
plot(groups_E, cex=0.9, hang=-1, main = "Euclidean", xlim = c(0, 10))
rect.hclust(groups_E, k=2)

## Cosine
groups_C <- hclust(dist_matrix_C,method="ward.D")
plot(groups_C, cex=0.9, hang=-1, main = "Cosine", xlim = c(0, 10))
rect.hclust(groups_C, k=2)

## Minkowski
groups_Min_1 <- hclust(dist_matrix_Min_1,method="ward.D")
plot(groups_Min_1, cex=0.9, hang=-1, main = "Manhattan", xlim = c(0, 10))
rect.hclust(groups_Min_1, k=2)
```

## K-means clustering

```{r}
description <- read.csv("paul_john_description_clean.csv")
description_unlabeled <- description %>% select(-Label)

# K-means clustering
description_matrix <- data.matrix(description_unlabeled)

## Silhouette........................
fviz_nbclust(description_matrix, method = "silhouette", 
             FUN = hcut, k.max = 9)

# for k = 2
## Run Kmeans...
My_Kmeans1 <- Kmeans(description_matrix, centers = 2, iter.max = 1000, method = "euclidean")
#, iter.max = 10, nstart = 1)
fviz_cluster(My_Kmeans1, description_matrix, main="Euclidean")

My_Kmeans2 <- Kmeans(description_matrix, centers = 2, iter.max = 1000, method = "spearman")
fviz_cluster(My_Kmeans2, description_matrix, main = "Spearman")

My_Kmeans3 <- Kmeans(description_matrix, centers = 2, iter.max = 1000, method = "manhattan")
fviz_cluster(My_Kmeans3, description_matrix, main ="Manhattan")

# for k = 4
## Run Kmeans...
My_Kmeans1 <- Kmeans(description_matrix, centers = 4, iter.max = 1000, method = "euclidean")
#, iter.max = 10, nstart = 1)
fviz_cluster(My_Kmeans1, description_matrix, main="Euclidean")

My_Kmeans2 <- Kmeans(description_matrix, centers = 4, iter.max = 1000, method = "spearman")
fviz_cluster(My_Kmeans2, description_matrix, main = "Spearman")

My_Kmeans3 <- Kmeans(description_matrix, centers = 4, iter.max = 1000, method = "manhattan")
fviz_cluster(My_Kmeans3, description_matrix, main ="Manhattan")

```

# News articles content

## Hierarchical clustering

```{r}
# Read in data

# setwd("C:/Users/maede/Downloads/R/INFO5653/Project/Project/INFO5653_Project")
full_text <- read.csv("paul_john_full_text_clean.csv")


# Save unlabeled data
full_text_unlabeled <- full_text %>% select(-Label)

# Find distances
dist_matrix_E <- dist(full_text_unlabeled, method="euclidean")

dist_matrix_C <- dist(full_text_unlabeled, method="cosine")

dist_matrix_Min_1 <- dist(full_text_unlabeled, method="manhattan", p=1)

# Hierarchical Clustering, Dendrogram

## Euclidean
groups_E <- hclust(dist_matrix_E,method="ward.D")
plot(groups_E, cex=0.9, hang=-1, main = "Euclidean", xlim = c(0, 10))
rect.hclust(groups_E, k=2)

## Cosine
groups_C <- hclust(dist_matrix_C,method="ward.D")
plot(groups_C, cex=0.9, hang=-1, main = "Cosine", xlim = c(0, 10))
rect.hclust(groups_C, k=2)

## Minkowski
groups_Min_1 <- hclust(dist_matrix_Min_1,method="ward.D")
plot(groups_Min_1, cex=0.9, hang=-1, main = "Manhattan", xlim = c(0, 10))
rect.hclust(groups_Min_1, k=2)
```

## K-means clustering

```{r}
full_text <- read.csv("paul_john_full_text_clean.csv")
full_text_unlabeled <- full_text %>% select(-Label)

# K-means clustering
full_text_matrix <- data.matrix(full_text_unlabeled)


## Silhouette........................
fviz_nbclust(full_text_matrix, method = "silhouette", 
             FUN = hcut, k.max = 9)

# for k = 2
## Run Kmeans...
My_Kmeans1 <- Kmeans(full_text_matrix, centers = 2, iter.max = 1000, method = "euclidean")
#, iter.max = 10, nstart = 1)
fviz_cluster(My_Kmeans1, full_text_matrix, main="Euclidean")

My_Kmeans2 <- Kmeans(full_text_matrix, centers = 2, iter.max = 1000, method = "spearman")
fviz_cluster(My_Kmeans2, full_text_matrix, main = "Spearman")

My_Kmeans3 <- Kmeans(full_text_matrix, centers = 2,iter.max = 1000, method = "manhattan")
fviz_cluster(My_Kmeans3, full_text_matrix, main ="Manhattan")

# for k = 2
## Run Kmeans...
My_Kmeans1 <- Kmeans(full_text_matrix, centers = 5, iter.max = 1000, method = "euclidean")
#, iter.max = 10, nstart = 1)
fviz_cluster(My_Kmeans1, full_text_matrix, main="Euclidean")

My_Kmeans2 <- Kmeans(full_text_matrix, centers = 5, iter.max = 1000, method = "spearman")
fviz_cluster(My_Kmeans2, full_text_matrix, main = "Spearman")

My_Kmeans3 <- Kmeans(full_text_matrix, centers = 5,iter.max = 1000, method = "manhattan")
fviz_cluster(My_Kmeans3, full_text_matrix, main ="Manhattan")

```